---
title: "Part 2: How to install Stata packages"
author: 
  - "Lars Vilhuber"
  - "Marie Connolly"
date: "`r Sys.Date()`"
output: 
  ioslides_presentation:
  incremental: false
self-included: true
widescreen: true
---
  
```{r, child=c('toc.md')}
```

## Overview

::: {.columns-2}

:::: {.column}

- Stata packages need to be installed

::::
  
:::: {.column}

- There are many ways to install them!
- Only a few lead to reproducible code!

::::
  
:::

# Installing Stata packages

## From the GUI

- Many people point and click - first search

[how to install packages - the GUI way](images/stata-gui-search.png)

## Then see the result

[how to install packages - the GUI way](images/stata-gui-search2.png)

## Then click to install

[how to install packages - the GUI way](images/stata-gui-install.png)

## From the command line

```
search adoinstall
ssc install adoinstall
```

## From the command line

```
net install st_0034, from("http://statajournal.com/sj/1/2")
```

# But where does it go?

Do you know?

## It goes here

```
. adopath
  [1]  (BASE)      "/usr/local/stata17/ado/base/"
  [2]  (SITE)      "/usr/local/ado/"
  [3]              "."
  [4]  (PERSONAL)  "~/ado/personal/"
  [5]  (PLUS)      "~/ado/plus/"
  [6]  (OLDPLACE)  "~/ado/"

```

## Or here

```
. adopath
  [1]  (BASE)      "C:\Program Files\Stata17\ado\base/"
  [2]  (SITE)      "C:\Program Files\Stata17\ado\site/"
  [3]              "."
  [4]  (PERSONAL)  "C:\Users\lv39\ado\personal/"
  [5]  (PLUS)      "C:\Users\lv39\ado\plus/"
  [6]  (OLDPLACE)  "c:\ado/"

```

## Where DID it go?

```
. which adoinstall
C:\Users\lv39\ado\plus\a\adoinstall.ado
*! version 0.1 5Aug2020
```

## What are the problems?

- Single place on disk where it is installed
  - Can you see the problem if you have multiple projects?
- The place where it is installed is not related to the project
  - How do I convey to replicators which package is needed?
  - ... and the version of the package
- The point-and-click or manual install are tedious
  

# Solution

Use **code** to install to a **project-specific location**.

## Solution

```
cd "$rootdir"
// Remove those unnecessary places
adopath - OLDPLACE
adopath - PLUS
adopath - PERSONAL
// Add a project specific one
cap mkdir adofiles
adopath ++ "${rootdir}/adofiles"
```

## Outcome

(note the search order)

```
. adopath ++ "${rootdir}/adofiles"
  [1]              "/path/to/project/adofiles"
  [2]  (BASE)      "C:\Program Files\Stata17\ado\base/"
  [3]  (SITE)      "C:\Program Files\Stata17\ado\site/"
  [4]              "."
```

## Next

How do we set `$rootdir` ?

## Next


```{r, child=c('toc.md')}
```
